### 2010-03-25 docs/architecture/architecture.tex
more on running

Some of the test problems available are:
\begin{itemize}
\item {\tt flame}
\item {\tt planar\_heat}
\item {\tt spherical\_heat}
\item {\tt test2}
\item {\tt test\_convect}
\item {\tt test\_spherical}
\end{itemize}

>>>>

Some of the test problems available are:
\begin{itemize}
\item {\tt flame} \\[-3mm]

The {\tt flame} problem models a planar laminar flame.  Initially cool
fuel and hot ash are put in pressure equilibrium.  Thermal diffusion
transfers heat to the fuel, driving a burning front.

\item {\tt planar\_heat} \\[-3mm]

\item {\tt spherical\_heat} \\[-3mm]

\item {\tt test2} \\[-3mm]

{\tt test2} places 3 hots spots in a plane-parallel atmosphere.
Burning makes these buoyant bubbles which role up.  This problem was
used in \cite{lowMach3} to compare with compressible solvers.

\item {\tt test\_convect} \\[-3mm]

\item {\tt test\_spherical} \\[-3mm]
\end{itemize}

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  Each problem
will have one or more inputs files (for example, {\tt test2/inputs\_2d}
which override the default values for one or more runtime parameters.
The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
